\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath, amssymb, amsthm, graphicx, hyperref}
\usepackage{enumerate}
\usepackage{fancyhdr}
\usepackage{multirow, multicol}
\usepackage{tikz}
\pagestyle{fancy}
\fancyhead[RO]{Eliot Brown Spring 2020}
\fancyhead[LO]{MA-UY 2314: Discrete Mathematics}
\usepackage{comment}
\newif\ifshow
\showfalse

\begin{document}

\begin{center}
\ifshow
  \textbf{\Large Homework 0 Solution}\\
\else
  \textbf{\Large Homework 3}\\
\fi
Due: Friday, Feb.. 21, by 11:59pm,\\via Gradescope\\
%Late HW accepted until 9PM on September 8\footnote{For each hour your homework is late, 10 points (out of 100) will be deducted from your homework score.  Please submit your homework on time!}
\end{center}

\hrule

\vspace{0.2cm}
\noindent
\begin{enumerate}[A.]
\item Refer to the Gradescope videos on YouTube if you have questions on how to submit homework.  
\item I refer you to the syllabus for the rubric that is used on the homework.  
\end{enumerate}




\begin{enumerate}
    \item (6 points) Section 8:  8.7(a), 8.9.  Explain your answers. \\ 
    \textbf{Solution 8.7a} $31!$ as order matters with 30 photos in 2 places. As it is not ordered, k photos can be put into the family album and 30-k photos will then be put into the friends album. There are then $(30-k)!$ ways to organize the photos in the friends album and $30*29*... 30-k+1$ amount of ways to organize the family album. For instance with 3 photos in the Family album there will be $30*29*28$ ways, and then with 27 photos in the friends album there will be 27! ways. Through the multiplication rule to include all possibilities of k out of the photos, this then results in $31*30! = 31!$ ways. \\
    
    \textbf{Solution 8.9} $7!*64$ or 3136 or $7*7*8*8$, as 7 other places in a row, for each row, then 64 places on the board, then using the multiplication rule to combine these amount of ways. \\
    
    
    \item (6 points) Section 8:   8.16, 8.19.  Explain your answers. \\ 
    \textbf{Solution 8.16}  $10*7^3$, first choice * 7 remaining options for the last 3. Consecutive cannot be the same # or next to so its a 4 digit list 0-10. There are 3,430 diﬀerent combinations. The ﬁrst number has 10 digits to choose from. Since numbers cannot repeat and numbers cannot be adjacent(a number has 2 adjacent numbers at any given time), this means that the second number has 7 options to choose from. The third number also has 7 options. The fourth number also 7 options. \\
    
    
    \textbf{Solution 8.19} There are 4 cards from the deck and if all are different values then when you pick one the next cannot be the same number, or the suit so you subtract 12, for the suit, and 4 for the same card value. So this means there is $52*36*22*10$ ways. 
    
    
    
    \item (3 points) List 2655 consecutive composite numbers.  Show that they are indeed composite.  \\
    
    \textbf{Solution} NTS: b $\exists$  s.t.  1 < b < 3000! + b  where  $ k = 2, ..., 2657 $ where  b|3000!+b and $x = 3000!+b $ so b|x. $ $ This will then show that all of the values of x are then consecutive composite numbers. \\
    
    
    
    
    \item (3 points) Let $A = 2^{\emptyset}, \; B = 2^{A}, C = 2^{B}$, and $D = 2^{C}$.  Construct D.   
    
        

    \textbf{D:}\\
    \noindent{} \{\\
    \emptyset,
    {\{\emptyset\}},   \{\emptyset,\{\emptyset\}\},    \{\{\emptyset\}\},    \{\{\{\emptyset\}\}\} \\
    \{\emptyset,\{\emptyset,\{\emptyset\}\}\},  \{\emptyset,\{\emptyset\}\},  \{\emptyset,\{\{\emptyset\}\}\},  \{\{\emptyset,\{\emptyset\}\},\{\emptyset\}\},\\
    \{\{\emptyset,\{\emptyset\}\},\{\{\emptyset\}\}\}, \{\{\emptyset\},\{\{\emptyset\}\}\},\\
    \{\emptyset,\{\emptyset,\{\emptyset\}\},\{\emptyset\}\}, \{\emptyset,\{\emptyset,\{\emptyset\}\},\{\{\emptyset\}\}\}\\
    \{\emptyset,\{\emptyset\},\{\{\emptyset\}\}\}, \{\{\emptyset,\{\emptyset\}\}\},\{\emptyset\},\{\{\emptyset\}\}\},
  
    \}

    
    
    
    
    \item (18 points) Section 10:  10.1(g), 10.3(c)(d)(e)(f)(g).  \\
    \noindent(10.1 (g)) \\
    \{\emptyset,\{1\},\{2\},\{3\},\{4\},\{5\} \}\\
    
    \noindent(10.3) \\(c)  \\
    0. There are no numbers contained in the empty set so the carnality of it will have to be zero.
    
    \noindent(d)\\
    $0$
    
    \noindent(e)\\
    \infty
     
    \noindent(f)\\
    $2^8$
     
    \noindent(g)\\
    $4$
    
    
    
    \item (21 points) Section 10: 10.4, 
    
    \textbf{Solution} 
     \noindent A: $2 \epsilon \{1,2,3\}$ \\
     \noindent B: $\subseteq$ \\
     \noindent C: $\epsilon$ \\ 
     \noindent D: $\subseteq$ \\ 
     \noindent E: $\subseteq$ \\
     \noindent F: $\subseteq$ \\
     \noindent G: $\epsilon$ \\
    
    
    
    
    \item (24 points) Section 10: 10.5, 10.6
    
    \textbf{Solution 10.5} \\
    \noindent A: $A = \emptyset$ \;\; $B = \{1\}$ \;\; $C=\{1,2,3\}$ \\
    \noindent B: $A = \{1\}$ \;\; $B = \{\{1\}\}$ \;\; $C=\{\{1\},2\}$ \\
    \noindent C: $A = \{1\}$ \;\; $B = \{\{1\}\}$ \;\; $C=\{\{\{1\}\}\}$ \\
    \noindent D: $A = \{1\}$ \;\; $B = \{1, 2\}$ \;\; $C=\{\{1,2\},3\}$ \\
    
    
    \textbf{Solution 10.6} \\
    \noindent A: $A = \{1 \}$ as $\emptyset$ exists in all sets \\ 
    \noindent B: $A = \{1\}$ \\
    \noindent C: $A=\emptyset$ \\
    \noindent D: No solution as set A can never exists in $\emptyset$ \\
    

    
    \item (9 points) 10.12, 10.14, 10.15.  
    
    \textbf{Solution 10.12} Let $C=\{x \epsilon \mathbb{Z} : x| 12 \} \wedge  D= \{x \epsilon \mathbb{Z}: x|36 \}$ Prove C $\subseteq$ D \\
    NTS: \\
       $\bullet$ If $x \epsilon C \rightarrow x \epsilon D$ \\
       \[
\begin{aligned} 
 x \epsilon C \\
&=  x|12\;\; \\ 
&=  12 = kx \;\;\;\;\; k \epsilon \mathbb{Z}\\
&= 36 = 3kx\;\; \\
&= 36 = mx \;\;\;\;\; m \epsilon 3k\\
&= x|36 \\
\square \\
\end{aligned}
\]
 
    
    
    \textbf{Solution 10.14}
    Give a value of x where the following is true:
           \[
\begin{aligned} 
 x \subseteq \{x\}\\
&=  x = \emptyset \;\; \\ 
&= \emptyset \subseteq \{\emptyset\} \;\;\;\;\;  \\
\square \\
\end{aligned}
\]
    
    \textbf{Solution 10.15}
    Show that T $\neq$ P:\\
    Let $x= \left( 0,1,-1\right)$ where $x \epsilon P$\\ 
    Then x $\epsilon$ P(a,b,c) cannot belong to T(p,q,r) \\
    $ p = 0, q = 1, r = -1$
    r must be non negative as in T: $r = x^2 + y^2$ \\ 
    Also as in T, $q=2xy$ for which $1=2x*y$ has no solutions for integers x,y. 
   
    
    \item (6 points)  Let 
    \[    
    \begin{aligned}
    A &= \{ x \in \mathbb{Z}: x = 6k -5 \mbox{ for some } k \in \mathbb{Z} \} \\
    B &= \{ x \in \mathbb{Z}: x = 3m + 1 \mbox{ for some } m \in \mathbb{Z} \} \\
    \end{aligned}
    \]
    \begin{enumerate}
        \item Is $A \subseteq B$?  If so, prove it.  If not, provide an appropriate counter-example.  Show that your counter-example works, i.e. show that your counterexample belongs to $A$ however does not belong to $B$.  \\
        
        \textbf{Solution} Prove if $A\subseteq B$ \\
        NTS: $x \epsilon A \rightarrow x \epsilon B$
            \[
\begin{aligned} 
Assume: x \epsilon A \wedge x \epsilon \mathbb{Z} \\
 x = 6k -5 \;\;\;\;\;\;\;\;\; k \epsilon \mathbb{Z} \\
&=  6k(+6-6) -5\;\; \\ 
&= (6k-6) +1 \;\;\;  \\
&= 3(2k-2) +1 \;\;\; m = 2k-2 \\
&= 3m+1 \\
\square \\
\end{aligned}
\]
        
        \\
        \\
        
        \item  Is $B \subseteq A$?  If so, prove it.  If not, provide an appropriate counter-example.  Show that your counter-example works, i.e. show that your counterexample belongs to $B$ however does not belong to $A$.  \\
        
        \textbf{Solution} Is $B \subseteq A$ \\
        x = 4 \\
        B: $4 = 3m +1$ \;\;\; $ m = 2k-2$ \\
        $4 = 3(2k - 2) +1$ \\ 
        $4 = 6k -6 +1$ \\
        $9 = 6k$  \\
        $6|9$ does not work, therefore B is not a subset of A \\
        \square
        
    \end{enumerate}
    \end{enumerate}
\end{document}


